# Transfer


## Purpose Of These Tables:
- A limiting factor for my transfer credit usage is that I am already at the allowed 60 credit capacity.
- I want to illustrate that we have room for removing credits from my transfer profile which do not fill any requirements.
- This makes room to add credits from my international experience to the transfer profile, which was not considered initially by mistake.
- This will also make room for other additions, preferably from my existing credits, but also from local colleges if necessary.  Many courses which I have already taken, as I now understand, have close equivalents in Cornell and in CALS.




## Total Eligible Transfer Credits
These are all of my courses which qualify for transfer, which recieved a passing grade.

```{r totaltransfer}
echo=FALSE

datatable(Total_Transfer_Requirement_Breakdown_Total_Transfer_Credits_Available)
```

## Current Transfer Profile
These are the courses which Cornell has already approved.

``` {r currenttransfer}
echo=FALSE

datatable(Total_Transfer_Requirement_Breakdown_Current_Transfer_Profile)

```

## Courses Currently Filling Requirements
These are the courses which are currently filling degree requirements.  Note that my main point is the difference between currently approved credits and requirement-filling credits.

```{r reqfilltransfer}
echo=FALSE

datatable(Total_Transfer_Requirement_Breakdown_Filling_Requirements)
```




